Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-21 vesicle_code/docs/adhesion/adhesion.tex
added a cartoon figure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers
adhesion between a single three-dimensional vesicle and a solid wall at
$z=0$.  \todo[inline]{Need a cartoon picture in here.  Some kind of
version of the one I had for my SIAM Life Sciences Talk} The adhesion
potential in their model is of the functional form in
equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$H$ is the Hamaker constant, and $\delta$ is the adhesion length
scale.  We generalize this model to an unbounded suspension of vesicles.
We assume that the adhesion force applies between all pairs of points on
different vesicles, so we are interested in Hamaker constants that are
appropriate for lipid-lipid interactions. In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-H m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}

%\begin{align}
%  \AA\xx:=-4 H \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
%  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
%  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
%  \label{eqn:adhesionForce}
%\end{align}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers
adhesion between a single three-dimensional vesicle and a solid wall at
$z=0$.  The adhesion potential in their model is of the functional form
in equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$H$ is the Hamaker constant, and $\delta$ is the adhesion length
scale.  We generalize this model to an unbounded suspension of vesicles.
We assume that the adhesion force applies between all pairs of points on
different vesicles, so we are interested in Hamaker constants that are
appropriate for lipid-lipid interactions. In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-H m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

\begin{figure}[htp]
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/configCartoon.pdf}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances in the
  green region are repulsive and distances in the blue region are
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked in with a red dot is repelled by the green region and
  attracted to the blue region.  The net forces are plotted with the
  black arrows.}
\end{figure}
